Ground state energy of quantum dots using the coupled cluster method

### 2018-05-24 project_2/article/article.tex
Move Wick's to appendix

		Now comes the rather tedious task of evaluating all the terms 
		that arises from inserting \autoref{eq:normal_order_expansion}
		into \autoref{eq:doubles_amplitude_1}. The first of such terms
		is
		\begin{equation}
		\begin{aligned}
			\bra{\Phi_{ij}^{ab}} &(F_N + V_N)\ket{\Phi_0} \\
			 =& \sum_{pq}f_{pq}\bra{\Phi_0}\{a_i^\dagger a_j^\dagger a_ba_a\}\{a^\dagger_pa_q\}\ket{\Phi_0} \\
			 &+\frac{1}{4}\sum_{pqrs}\bra{pq}\ket{rs}
			 \bra{\Phi_0}\{a_i^\dagger a_j^\dagger a_ba_a\}\{a^\dagger_pa^\dagger_qa_sa_r\}\ket{\Phi_0}.
		\end{aligned}
		\end{equation}
		The one-electron component does not have any full contractions, while the
		two-electron component produces one contributing integral,
		\begin{equation}
		\begin{aligned}
			\bra{\Phi_{ij}^{ab}} &(V_N)\ket{\Phi_0} \\
				=& \frac{1}{4}\sum_{pqrs}\bra{pq}\ket{rs}
			 \bra{\Phi_0}\{a_i^\dagger a_j^\dagger a_ba_a\}\{a^\dagger_pa^\dagger_qa_sa_r\}\ket{\Phi_0} \\
			 	=& \frac{1}{4} \sum_{pqrs} \bra{pq}\ket{rs} \\ &\times\Big(
			 		\{ \wick{\c1 a^\dagger_i \c2 a^\dagger_j \c3 a_b \c4 a_a
			 		\c4 a^\dagger_p \c3 a^\dagger_q \c2 a_s \c1 a_r}\}
			 		+
			 		\{ \wick{\c1 a^\dagger_i \c2 a^\dagger_j \c4 a_b \c3 a_a
			 		\c4 a^\dagger_p \c3 a^\dagger_q \c2 a_s \c1 a_r}\} \\
			 	  &\ +
			 	 	\{ \wick{\c2 a^\dagger_i \c1 a^\dagger_j \c3 a_b \c4 a_a
			 		\c4 a^\dagger_p \c3 a^\dagger_q \c2 a_s \c1 a_r}\}
			 		+
			 		\{ \wick{\c2 a^\dagger_i \c1 a^\dagger_j \c4 a_b \c3 a_a
			 		\c4 a^\dagger_p \c3 a^\dagger_q \c2 a_s \c1 a_r}\}
			 	\Big) \\
			 	=&  \frac{1}{4} \sum_{pqrs} \bra{pq}\ket{rs} 
			 	( \delta_{ap}\delta_{bq}\delta_{js}\delta_{ir}
			 	 -\delta_{aq}\delta_{bp}\delta_{js}\delta_{ir} \\
			     &\ -\delta_{ap}\delta_{bq}\delta_{jr}\delta_{is}
			 	 +\delta_{aq}\delta_{bp}\delta_{jr}\delta_{is}) \\
			 	 =& \bra{ab}\ket{ij} = u^{ab}_{ij}.
		\end{aligned}
		\end{equation}
				 =& u_{cm}^{bm}t_{ij}^{ac}P(ab) + u_{jm}^{mk}t_{ik}^{ab}P(ij)
		Where in the last steps we have consigned the sums by Einstein summation notation.
		We have also only included the two-body part of the fock operator, because we are
		dealing with double excitations (relaxations) only.

		One could of course continue in this manner, employing Wick's general theorem to all
		terms that arises from combining \autoref{eq:normal_order_expansion}
		\autoref{eq:doubles_amplitude_1}, but because this task is quite strenuous, we employ
		the second quantisation library from SymPy instead\footnote{This is also more in the
		spirit of this project, as it is in the realm of \emph{Computational} Physics.}.
		The CCD amplitude equation, from SymPy computation, is 
		\begin{equation}
		\begin{aligned}
			0 =& u^{ab}_{ij} + t^{ac}_{ij} u^{bm}_{cm} P(ab) + t^{ab}_{ik} u^{mk}_{jsm} P(ij) \\
				 +& \frac{1}{4}t^{cd}_{ij} t^{ab}_{nm} u^{nm}_{cd} + \frac{1}{2}t^{cd}_{ij} u^{ab}_{cd} \\
				 -& \frac{1}{2}t^{cd}_{jm} t^{ab}_{in} u^{nm}_{cd} P(ij) - \frac{1}{2}t^{ac}_{nm} t^{bd}_{ij} u^{nm}_{cd} P(ab) \\
				 -& t^{ac}_{im} t^{bd}_{jn} u^{nm}_{cd} P(ij) + t^{ac}_{im} u^{bm}_{jc} P(ab) P(ij) \\
				 +& \frac{1}{2}t^{ab}_{nm} u^{nm}_{ij}, 
		\end{aligned}
		\end{equation}

		where we recognize the first three terms.

@@

>>>>

		Now comes the rather tedious task of evaluating all the terms 
		that arises from inserting \autoref{eq:normal_order_expansion}
		into \autoref{eq:doubles_amplitude_1}. This can be done by applying
		Wick's generalised theorem, but the task is a daunting and streneous one.
		A few example computations of how this can be done is included in
		\autoref{app:wickOnAmplitude}.
	 	Instead of doing it in this manner, we employ the second quantisation library
	 	from SymPy instead\footnote{This is also more in the spirit of this project,
	 	as it is within the realm of \emph{Computational} Physics.}.
		The CCD amplitude equation, from SymPy computation, is 
		\begin{equation}
		\begin{aligned}
			0 =& u^{ab}_{ij} + t^{ac}_{ij} u^{bm}_{cm} P(ab) + t^{ab}_{ik} u^{mk}_{jsm} P(ij) \\
				 +& \frac{1}{4}t^{cd}_{ij} t^{ab}_{nm} u^{nm}_{cd} + \frac{1}{2}t^{cd}_{ij} u^{ab}_{cd} \\
				 -& \frac{1}{2}t^{cd}_{jm} t^{ab}_{in} u^{nm}_{cd} P(ij) - \frac{1}{2}t^{ac}_{nm} t^{bd}_{ij} u^{nm}_{cd} P(ab) \\
				 -& t^{ac}_{im} t^{bd}_{jn} u^{nm}_{cd} P(ij) + t^{ac}_{im} u^{bm}_{jc} P(ab) P(ij) \\
				 +& \frac{1}{2}t^{ab}_{nm} u^{nm}_{ij}. 
		\end{aligned}
		\end{equation}

@@

\section{Amplitude Equations}

	\label{app:wickOnAmplitude}

	In this section we have provided a few sample computations of how one would
	evaluate the amplitude equations using wicks theorem. Starting with the simplest
	term including only the normal-ordered Hamiltonian,

	\begin{equation}
		\begin{aligned}
			\bra{\Phi_{ij}^{ab}} &(F_N + V_N)\ket{\Phi_0} \\
			 =& \sum_{pq}f_{pq}\bra{\Phi_0}\{a_i^\dagger a_j^\dagger a_ba_a\}\{a^\dagger_pa_q\}\ket{\Phi_0} \\
			 &+\frac{1}{4}\sum_{pqrs}\bra{pq}\ket{rs}
			 \bra{\Phi_0}\{a_i^\dagger a_j^\dagger a_ba_a\}\{a^\dagger_pa^\dagger_qa_sa_r\}\ket{\Phi_0}.
		\end{aligned}
		\end{equation}
		The one-electron component does not have any full contractions, while the
		two-electron component produces one contributing integral,
		\begin{equation}
		\begin{aligned}
			\bra{\Phi_{ij}^{ab}} &(V_N)\ket{\Phi_0} \\
				=& \frac{1}{4}\sum_{pqrs}\bra{pq}\ket{rs}
			 \bra{\Phi_0}\{a_i^\dagger a_j^\dagger a_ba_a\}\{a^\dagger_pa^\dagger_qa_sa_r\}\ket{\Phi_0} \\
			 	=& \frac{1}{4} \sum_{pqrs} \bra{pq}\ket{rs} \\ &\times\Big(
			 		\{ \wick{\c1 a^\dagger_i \c2 a^\dagger_j \c3 a_b \c4 a_a
			 		\c4 a^\dagger_p \c3 a^\dagger_q \c2 a_s \c1 a_r}\}
			 		+
			 		\{ \wick{\c1 a^\dagger_i \c2 a^\dagger_j \c4 a_b \c3 a_a
			 		\c4 a^\dagger_p \c3 a^\dagger_q \c2 a_s \c1 a_r}\} \\
			 	  &\ +
			 	 	\{ \wick{\c2 a^\dagger_i \c1 a^\dagger_j \c3 a_b \c4 a_a
			 		\c4 a^\dagger_p \c3 a^\dagger_q \c2 a_s \c1 a_r}\}
			 		+
			 		\{ \wick{\c2 a^\dagger_i \c1 a^\dagger_j \c4 a_b \c3 a_a
			 		\c4 a^\dagger_p \c3 a^\dagger_q \c2 a_s \c1 a_r}\}
			 	\Big) \\
			 	=&  \frac{1}{4} \sum_{pqrs} \bra{pq}\ket{rs} 
			 	( \delta_{ap}\delta_{bq}\delta_{js}\delta_{ir}
			 	 -\delta_{aq}\delta_{bp}\delta_{js}\delta_{ir} \\
			     &\ -\delta_{ap}\delta_{bq}\delta_{jr}\delta_{is}
			 	 +\delta_{aq}\delta_{bp}\delta_{jr}\delta_{is}) \\
			 	 =& \bra{ab}\ket{ij} = u^{ab}_{ij}.
		\end{aligned}
		\end{equation}
				 =& (h^c_b + u_{cm}^{bm})t_{ij}^{ac}P(ab) + (h^j_m + u_{jm}^{mk})t_{ik}^{ab}P(ij)
		Where in the last steps we have consigned the sums by Einstein summation notation,
		and split the Fock operator into one- and two-body parts.
